### 2018-01-29 ApproxComp/sec-query.tex

The compression ratios of lossless methods are poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}. Hence, lossy techniques, which  provide approximate solutions with good compression ratios and bounded errors, is the mainstream.

@@

The problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}. Even worse, it remains hard to approximate for temporal networks  with single snapshots~\cite{MaHWLH17}. Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty. The state of the art solution \kw{MEDEN} \cite{BogdanovMS11} adopts a filter-and-verification ({\kw{FAV}) framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}. Hence, this method is not big data friendly, and is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.

>>>>

The compression ratios of lossless methods are poor, and querying on the compressed data is time consuming due to the reconstruction of the original data \cite{Nibali:Trajic}. Hence, lossy techniques, which  provide approximate solutions with good compression ratios and bounded errors, are the mainstream.

@@

The problem of  finding dense subgraphs in temporal networks is non-trivial, and it is already \NP-complete even for a temporal network with a single snapshot and with $+1$ or $-1$ edge weights only, as observed in \cite{BogdanovMS11}. Even worse, it remains hard to approximate for temporal networks  with single snapshots~\cite{MaHWLH17}. Moreover, given a temporal network with $T$ timestamps, there are a total number of $T*(T+1)/2$ time intervals to consider, which further aggravates the difficulty. The state of the art solution \kw{MEDEN} \cite{BogdanovMS11} adopts a Filter-And-Verification ({\kw{FAV}) framework that {\em even if a large portion of time intervals are filtered, there often remain a large number of time intervals to verify}. Hence, this method is not big data friendly, and is not scalable when temporal networks have a large number of nodes/edges or a large number $T$ of timestamps.
